\begin{thebibliography}{99}
\addcontentsline{toc}{section}{Список литературы}
\bibitem{Braeken} {\it Braeken A., Wolf C., Preneel B.} A randomized algorithm for checking the normality of cryptographic boolean functions // “Exploring New Frontiers of Theoretical Informatics” as the proceedings of the “3rd International Conference on Theoretical Computer Science (TCS2004)”, Kluwer Academic Publishers, 2004.
\bibitem{Canteaut} {\it Canteaut A., Daum M., Dobbertin H., Leander G.} Finding nonnormal bent functions // Discrete Applied Mathematics 2006. Vol. 154, No. 2.
\bibitem{Cantenaut6}{\it Canteaut A., Daum M., Leander G., Dobbertin H.} Normal and non normal bent functions // Proceedings of the 2003 International Workshop on Coding and Cryptography (WCC 2003), Versailles, France, March 2003.
% \bibitem{CarletError} {\it Carlet C.}. Boolean Functions for Cryptography and Error Correcting Codes // Cambridge University Press, 2010.
\bibitem{CarletIncreaseN} {\it Carlet C.} On cryptographic complexity of boolean functions. // In Finite Fields with Applications to Coding Theory, Cryptography and Related Areas, 2002.
\bibitem{CarletCryptographic} {\it Carlet C.} The complexity of Boolean functions from cryptographic viewpoint. // Dagstuhl Seminar <<Complexity of Boolean Functions>> 2006.
%\bibitem{CarletGaborit} {\it Carlet C., Gaborit P.} Hyper–bent functions and cyclic codes // Journal of Combinatorial Theory, Series A 113 (2006).
\bibitem{Charpin} {\it Charpin P.} Normal Boolean functions // Journal of Complexity, Vol. 20, Issues 2–3, April–June 2004.
% \bibitem{Courtois} {\it Courtois N., Meier W.} Algebraic attacks on stream ciphers with linear feedback. // In Advances in Cryptology - EUROCRYPT 2003, number 2656 in Lecture Notes in Computer Science. Springer Verlag,  2003.
\bibitem{Cusick} {\it Cusick T. W., Stănică P.} Cryptographic Boolean Functions and Applications. // Academic Press - Elsevier, 2009.
% \bibitem{Daum} {\it Daum M., Leander G., Dobbertin H.} An algorithm for checking normality of Boolean functions. // Proceedings of the 2003 International Workshop on Coding and Cryptography (WCC 2003), March 2003, pp. 133–142.
% \bibitem{Didier} {\it Didier F.} A new upper bound on the block error probability after decoding over the erasure channel. // Preprint available at http://www-rocq.inria.fr/codes/Frederic.Didier/ A revised version will appear in IEEE Transactions on Information Theory, 2006.
\bibitem{Dillon} {\it Dillon J. F.} Elementary Hadamard Difference sets // Ph. D. Thesis, Univ. of Maryland, 1974.
\bibitem{Dobbertin} {\it Dobbertin H.} Construction of bent functions and balanced Boolean functions with high nonlinearity. // Fast Software Encryption, Lecture Notes in Computer Science, Vol. 1008, Springer, Berlin, 1994.
\bibitem{Gangopadhyay} {\it Gangopadhyay S., Sharma D.} On construction of non-normal Boolean functions. Australasian journal of combinatorics // Combinatorial Mathematics Society of Australasia), Vol. 38, 2007.
\bibitem{Leandr} {\it Leander G.} Another class of non-normal bent functions. Proceedings of the conference BFCA 2006, Publications des universit'es de Rouen et du Havre, 2006.
\bibitem{McFarland} {\it McFarland R. L.} A family of difference sets in non-cyclic groups // J. Combin. Theory. Ser. A. 1973. Vol. 15, No 1.
\bibitem{Mihaljevc} {\it Mihaljevic M., Gangopadhyay S., Goutam P., Hideki I.} Generic cryptographic weakness of k-normal boolean functions in certain stream ciphres and cryptoanalysis of GRAIN-128 // Periodica Mathematica Hungarica Vol. 65 (2), 2012.
\bibitem{Nowak} {\it Nowak K.} Checking normality of Boolean functions // Tatra Mt. Math. Publ. 33 (2006).
\bibitem{RothausFirst} {\it Rothaus O.} On bent functions // IDA CRD W.P. No. 169. 1976.
% \bibitem{RothausSecond}  {\it Rothaus O. S.} (May 1976). «On "Bent" Functions». Journal of Combinatorial Theory, Series A 20 (3): 300–305. DOI:10.1016/0097-3165(76)90024-8. ISSN 0097-3165.
\bibitem{Zhang} {\it Zhang W., Xiao G.} Checking normality of bent functions // ISN Laboratory, Xidian University, Xi’an 710071, China, 2009.
\bibitem{Agafonova} {\it Агафонова И. В.} Криптографические свойства нелинейных булевых функций. // Доклад на сайте dha.spb.ru, http://dha.spb.ru/PDF/cryptoBOOLEAN.pdf, 2007.
% \bibitem{ColomeecPhD} {\it Коломеец Н. А} Бент-функции, аффинные на подпространствах и их метрические свойства. // Диссертация на соискание учёной степени кандидата физико-математических наук.
% \bibitem{Colomeec} {\it Коломеец Н. А., Павлов А. В.} Свойства бент-функций, находящихся на минимальном расстоянии друг от друга // Прикладная Дискретная Математика, 2009, N 4.
% \bibitem{Logachev} {\it Логачев О.А., Сальников А.А., Ященко В.В.} Булевы функции в теории кодирования и криптологии. // Москва, МЦНМО 2004г. ISBN: 5-94057-117-4.
% \bibitem{TokarevaPhD} {\it Токарева Н.И.} Диссертация на соискание ученой степени кандидата физико-математических наук.
\bibitem{Tokareva} {\it Токарева Н. Н.} Нелинейные булевы функции: бент-функции и их обобщения // Издательство LAP LAMBERT Academic Publishing (Saarbrucken, Germany), 2011.

\end{thebibliography}
